Counterexamples in Mathematical Relations

### 2024-10-31 Relations/RewritingQs.tex
ARS-stuff
ARSwork

\usepackage{xcolor}

@@

@@

>>>>

\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{xcolor}

@@

\textbf{Primary Goal: A technical report that focuses on
Abstract Rewriting in Constructive Setting }

\section{2024.10.31}

Rewriting properties.
Elementwise
\begin{itemize}
  \item NF
  \item WN
  \item SN
  \item WCR
  \item CR
  \item NFP
  \item UN$\to$
  \item UN
  \item RP
  \item RP$-$
  \item $\omega$-bound
  \item Recurrent
  \item CP (Cofinality property)
  \item FB (Finite branching of rewrite steps)
  \item DominatedByWF (Needed?)
  \item Define WNFP to be:
  \[\forall a b c \to b \in NF \to a R^* b \to a R^* c \to c R^* b \]
  \item Does WNFP and WN imply CR?  Looks like it!
  \item Another interesting one? $WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$.)

  Could even consider $SN^*$, $CR^*$ etc.
\end{itemize}
Most of these properties $P$ have a ``global'' version $P^\forall$, asserting that $\forall x. P(x)$ holds.

Other properties that show up in classical ARS theory:
\begin{itemize}
  \item Inc
  \item Ind
  \item $\mathrm{CR}^{\le 1}$
\end{itemize}
Want to discuss these, and why we may or may not include them in our
development.

Outline of the document:
\begin{enumerate}
  \item Create a diagram with implications between these, and
  combinations of these, similar to the one in TeReSe.
  \item Formalization of valid implications
  \item Counterexamples: Compile a list/chart/graph of those relationships
  which can be disproved. (A big part!!)
  \item A list of classical properties, and elaboration of their meaning
  and whether it's reasonable to assume them in a rewriting context.
  (Discuss each, and its role in ARS theory.)
  \item Well-foundedness: different constructive formulations, and relationships between them
  \item ``Guide'' to the formalization code, GitHub repo
  \item Discussion of open problems (Add a subsection of these at the end of each section?)
  \item Conclusion
\end{enumerate}

\section{Established implications:}

\begin{itemize}
  \item SN implies $\omega$-bounded
\end{itemize}

@@

\section{Open problems}

\begin{itemize}
  \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.

  So, does $WN, RP, WCR$ imply $\omega$-bounded?
  Answer: yes, that is what we have proved classically.

  \item Wait, does RP- actually imply RP????

  \item RP- and $\omega$-bounded implies RP?
  \item RP- and WCR imply RP?
  \item
  \[ WNg \land UN \to CRelem :
  \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
  \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
\end{itemize}
